\thesistitle

### 2019-07-16 sections/clonerefactor.tex
Fixed stuff

\subsubsection{Conceptual method of removing redundant clone classes}
Using the method described in the this section, we find redundant clones. We remove these clones if they are a subset of an existant clone. We define the subset relation between clones as displayed as follows:

@@

\begin{equation}\label{eq:removeall}
S = S \setminus (C_{existing} \subseteq C_{new}\text{ }|\text{ }C_{existing} \in S)
\end{equation}

@@

\begin{equation}\label{eq:removeexisting}
(C_{existing} \subseteq C_{new}\text{ }|\text{ }C_{existing} \in S) = \emptyset \Rightarrow S = S \cup C_{new}
\end{equation}

For CloneRefactor, we used this conceptual method of removing duplicates, but did not directly implemented these equations. The main reason for this is the runtime overhead, as this process has to iterate over each existing clone class and each of their clone instances. For large projects with a lot of duplication this process has a significant impact on performance.

\subsubsection{Method of removing redundant clone classes}
\todo{Write this section}

>>>>

\subsubsection{Conceptual method of removing redundant clone classes}
The clone detection method used by CloneRefactor can, for various reasons,%Should I list these? Listing them could be a section on its own, as I'd have to show examples to make it concrete.
result in redundant clone classes. After the insertion of each newly detected clone, we check whether it is redundant and/or any of the existent clones has become redundant by adding this clone. A clone is redundant if it is a subset of an existing clone. We define the subset relation between clones as follows:

@@

\begin{equation}\label{eq:removeall}
S = S \setminus \{C_{existing} \subseteq C_{new}\text{ }|\text{ }C_{existing} \in S\}
\end{equation}

@@

\begin{equation}\label{eq:removeexisting}
\{C_{existing} \subseteq C_{new}\text{ }|\text{ }C_{existing} \in S\} = \emptyset \Rightarrow S = S \cup C_{new}
\end{equation}

For CloneRefactor we used this conceptual method of removing duplicates, but did not directly implement these equations. The main reason for this is the runtime overhead, as this process has to iterate over each existing clone class and each of their clone instances. For large projects with a lot of duplication this process has a significant impact on performance.

\subsubsection{CloneRefactor method of removing redundant clone classes}
